---
title: "FISH_3D_Distance"
author: "Gianluca Pegoraro"
date: "Dec 21, 2015"
output: html_document
---

```{r}
library('hexbin')
library('plyr')
library('ggplot2')
library('stringr')
library('knitr')
library('reshape2')
library('data.table')
```

```{r, include=FALSE, warning=FALSE}
opts_chunk$set(fig.path='R_Output/', cache = FALSE, cache.path='cache_final/', dev=c("png"), dpi = 600, fig.width=7, fig.height=7, message=FALSE, warning=FALSE)
```

Specify x,y pixel size (microns) and z-step (microns)

```{r setResolution}
xyres <- 0.10833333
zstep <- 0.5
```

### Read and Process the Experimental Metadata

A file named `GlobalLayout.txt` should be present in the `ExperimentalMetadata` sub directory. This file should contain information about the treatments for each well.  While the file for all the wells in the single-spot data will be read in,  `GlobalLayout.txt` will select the wells to be used for analysis and plotting. If a well is not specified in the `GlobalLayout.txt`, it won't be output. 

```{r readMetadata, results='asis'}
dt.md <- fread('ExperimentalMetadata/GlobalLayout.txt', 
               colClasses=c("integer", "integer", "double", "double", "double", "integer", "character", "character"))
setkey(dt.md, nrow, ncol)

dt.md <- dt.md[Green_Probe != '',] # Filter out unannotated wells
kable(dt.md)
```


### Read the Object Level Data

Set RegEx patterns for directory searches for cell level data and spot data in all colors.
```{r regexFilename, results='hide'}
pat.n <- "spot_positions.csv$"
```

Create a list of the RegEx patterns set in the previous chunk. **Important:** the list names will be carried over all the next steps!!!

* c = cell level data
* g = Green Spot data
* r = Red Spot data
* f = FarRed Spot data

```{r patList, results = 'hide'}
pat.list <- list(all = pat.n)
```

Recursively search the `ObjectLevelData` directory and its subdirectories for files whose name includes the RegEx patterns defined two chunks above. The `path.list` functon outputs absolute file names. `path.list` is a list containing all the filenames on a per cell-level or per color-level (i.e. gr, gf or fr) basis.
```{r directorySearch, results='hide'}
list.files <- function(x){
  dir(path = 'ObjectLevelData', pattern = x, full.names = TRUE, recursive = TRUE, include.dirs = TRUE)
}

path.list <- llply(pat.list, list.files) 
```

Extract file names from absolut path and set them as list element names. 
```{r trimNames, results='hide'}
trim.names <- function(x){
  names(x) <- basename(x) # This assigns the filename to the file that it is read
  y <- x ## This is necessary because of scoping issues
}

path.list <- llply(path.list, trim.names) 
```

Recursively read and merge object level data files as data.frames. Rows are labeled with relative filenames (The `.id` variable). This and the previous chunks are slightly modified tricks adopted from H. Wickam ["Tidy Data" paper](http://vita.had.co.nz/papers/tidy-data.pdf).

```{r readMerge, results='hide'}
read.merge <- function(x){
  dt <-as.data.table(ldply(x, fread)) 
}

dt.list <- llply(path.list, read.merge)
```

Separate the cell level data from the distance and spot level data.

```{r deleteDtList, results='asis'}
dt.all <- dt.list$all
```

### Process the object-level data

Rename the appropriate variables to allow for downstream inner-join operations.

```{r renameVariables}
setnames(dt.all,    c(".id",
                    "filename",
                    "experiment",
                    "well",
                    "timepoint",
                    "field",
                    "timeline",
                    "channel",
                    "nucleus_index",
                    "spot_index",
                    "center_x",
                    "center_y",
                    "center_z",
                    "center_r",
                    "nuclear_mask_offset_x",
                    "nuclear_mask_offset_y"),
                  c(".id",
                    "filename",
                    "AssayIndex",
                    "Well",
                    "timepoint",
                    "FieldIndex",
                    "timeline",
                    "channel",
                    "CellIndex",
                    "SpotIndex",
                    "x.cog",
                    "y.cog",
                    "z.cog",
                    "r.cog",
                    "x.offset",
                    "y.offset"))


dt.all[,`:=`(color = factor(channel, levels=c(2,3,4), labels=c("Green", "Red", "Far Red")),
             nrow = as.integer(factor(x = regmatches(Well, regexpr("[[:upper:]]{1}", Well)), 
                                   levels=c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", "N", 
                                            "O", "P"),
                                   labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16))),
             ncol = as.integer(regmatches(Well, regexpr("[[:digit:]]{2}", Well))))]

```

## Add Cell level data (number of spots per channel per cell) to spot level data.

Calculate the number of spots per cell:
```{r calcSpotsPerCell}
dt.cell <- dt.all[,list(GreenSpotCount = sum(color=="Green"),
                        RedSpotCount = sum(color=="Red"),
                        FarRedSpotCount = sum(color=="Far Red")),
                  by = list(nrow, ncol, FieldIndex, CellIndex)]

dt.cell[,`:=`(PercDiploidGreen = sum(GreenSpotCount == 2)/.N,
             PercDiploidRed = sum(RedSpotCount == 2)/.N,
             PercDiploidFarRed = sum(FarRedSpotCount == 2)/.N), by = list(nrow, ncol)]

setkey(dt.cell, nrow, ncol, FieldIndex, CellIndex)
setkey(dt.all, nrow, ncol, FieldIndex, CellIndex)

dt.all <- dt.all[dt.cell]
```

Crossreference metadata for probe list.

```{r metadataExtract, results='hide'}
## Set common keys on all data.tables, both cell and spot levels
dt.all <- setkey(dt.all, nrow,ncol)
dt.cell <- setkey(dt.cell, nrow, ncol)

## Merge all data.tables with the experimental metadata tables via inner join (wells not present in both tables are ignored)
dt.all <- dt.all[dt.md, nomatch = 0] 
dt.cell <- dt.cell[dt.md, nomatch=0]

## Set common keys on all data.tables, both cell and distance levels
dt.all <- setkey(dt.all, nrow, ncol, FieldIndex, CellIndex, Green_Probe, Red_Probe, FarRed_Probe, chr, Cell_Type, Culture_Condition)
dt.cell <- setkey(dt.cell, nrow, ncol, FieldIndex, CellIndex, Green_Probe, Red_Probe, FarRed_Probe, chr, Cell_Type, Culture_Condition)
```

### Calculate Minimum Distances and Paired Spots Events.

```{r}
dt.gr <- dt.all[color %in% c("Green", "Red"),]
setkey(dt.gr, nrow, ncol, FieldIndex, CellIndex)

dt.gf <- dt.all[color %in% c("Green", "Far Red"),]
setkey(dt.gf, nrow, ncol, FieldIndex, CellIndex)

dt.rf <- dt.all[color %in% c("Red", "Far Red"),]
setkey(dt.rf, nrow, ncol, FieldIndex, CellIndex)
```

Select only Distances from cells that have equal numbers of Red and Green spots. This filtering makes the only assumption that in each cell the FISH should have worked for Green and Red. No assumption is made on the ploidy or phase of the cell cycle of the specific cell. (all spots > 1 per cell, spot counts equal)

```{r selectDistances, results= 'hide'}
dt.gr.sel <- dt.gr[GreenSpotCount > 1 & RedSpotCount > 1 & 
                     (GreenSpotCount == RedSpotCount) & PercDiploidRed > 0.5 & PercDiploidGreen > 0.5,]
dt.gf.sel <- dt.gf[GreenSpotCount > 1 & FarRedSpotCount > 1 & 
                     (GreenSpotCount == FarRedSpotCount) & PercDiploidFarRed > 0.5 & PercDiploidGreen > 0.5,]
dt.rf.sel <- dt.rf[FarRedSpotCount > 1 & RedSpotCount > 1 & 
                     (FarRedSpotCount == RedSpotCount) & PercDiploidRed > 0.5 & PercDiploidFarRed > 0.5,]

dt.all.sel <- rbindlist(list(dt.gr.sel, dt.gf.sel[color == "Far Red",]))
```

Calculate 2D spot distances.

```{r SpotDist, results='hide'}
# Create holder table with possible combinations of spot indexes, rename columns as needed
dt.gr.dist <- dt.gr.sel[,expand.grid(c(1:max(GreenSpotCount)-1), c(1:max(RedSpotCount)-1)), 
                        by=list(AssayIndex, nrow,ncol, 
                                Green_Probe, Red_Probe, FarRed_Probe, chr, Cell_Type, Culture_Condition,
                                FieldIndex, CellIndex, 
                                PercDiploidGreen, PercDiploidRed, PercDiploidFarRed)]

setnames(dt.gr.dist, c("Var1", "Var2"), c("SpotIndex1", "SpotIndex2"))

dt.gf.dist <- dt.gr.sel[,expand.grid(c(1:max(GreenSpotCount)-1), c(1:max(FarRedSpotCount)-1)), 
                        by=list(AssayIndex, nrow,ncol, 
                                Green_Probe, Red_Probe, FarRed_Probe, chr, Cell_Type, Culture_Condition,
                                FieldIndex, CellIndex, 
                                PercDiploidGreen, PercDiploidRed, PercDiploidFarRed)]

setnames(dt.gf.dist, c("Var1", "Var2"), c("SpotIndex1", "SpotIndex2"))

dt.rf.dist <- dt.gr.sel[,expand.grid(c(1:max(RedSpotCount)-1), c(1:max(FarRedSpotCount)-1)), 
                        by=list(AssayIndex, nrow,ncol, 
                                Green_Probe, Red_Probe, FarRed_Probe, chr, Cell_Type, Culture_Condition,
                                FieldIndex, CellIndex, 
                                PercDiploidGreen, PercDiploidRed, PercDiploidFarRed)]

setnames(dt.rf.dist, c("Var1", "Var2"), c("SpotIndex1", "SpotIndex2"))

## Add in spot positions in all four dimensions and channel assignments
# Green - Red
setkey(dt.gr.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex1)
setkey(dt.gr.sel, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex)
dt.gr.dist <- dt.gr.dist[dt.gr.sel[color=="Green",list(AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex, 
                                                         x.cog, y.cog, z.cog, r.cog)],nomatch=0]
setnames(dt.gr.dist, c("x.cog", "y.cog", "z.cog", "r.cog"), c("Spot1.x.cog", "Spot1.y.cog", "Spot1.z.cog", "Spot1.r.cog"))

setkey(dt.gr.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex2)
dt.gr.dist <- dt.gr.dist[dt.gr.sel[color=="Red",list(AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex, 
                                                         x.cog, y.cog, z.cog, r.cog)],nomatch=0]
setnames(dt.gr.dist, c("x.cog", "y.cog", "z.cog", "r.cog"), c("Spot2.x.cog", "Spot2.y.cog", "Spot2.z.cog", "Spot2.r.cog"))

dt.gr.dist[,`:=`(Channel1="Green",
                 Channel2="Red")]

# Green - Far Red
setkey(dt.gf.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex1)
setkey(dt.gf.sel, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex)
dt.gf.dist <- dt.gf.dist[dt.gf.sel[color=="Green",list(AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex, 
                                                         x.cog, y.cog, z.cog, r.cog)],nomatch=0]
setnames(dt.gf.dist, c("x.cog", "y.cog", "z.cog", "r.cog"), c("Spot1.x.cog", "Spot1.y.cog", "Spot1.z.cog", "Spot1.r.cog"))

setkey(dt.gf.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex2)
dt.gf.dist <- dt.gf.dist[dt.gf.sel[color=="Far Red",list(AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex, 
                                                         x.cog, y.cog, z.cog, r.cog)],nomatch=0]
setnames(dt.gf.dist, c("x.cog", "y.cog", "z.cog", "r.cog"), c("Spot2.x.cog", "Spot2.y.cog", "Spot2.z.cog", "Spot2.r.cog"))

dt.gf.dist[,`:=`(Channel1="Green",
                 Channel2="Far Red")]

# Red - Far Red
setkey(dt.rf.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex1)
setkey(dt.rf.sel, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex)
dt.rf.dist <- dt.rf.dist[dt.rf.sel[color=="Red",list(AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex, 
                                                         x.cog, y.cog, z.cog, r.cog)],nomatch=0]
setnames(dt.rf.dist, c("x.cog", "y.cog", "z.cog", "r.cog"), c("Spot1.x.cog", "Spot1.y.cog", "Spot1.z.cog", "Spot1.r.cog"))

setkey(dt.rf.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex2)
dt.rf.dist <- dt.rf.dist[dt.rf.sel[color=="Far Red",list(AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex, 
                                                         x.cog, y.cog, z.cog, r.cog)],nomatch=0]
setnames(dt.rf.dist, c("x.cog", "y.cog", "z.cog", "r.cog"), c("Spot2.x.cog", "Spot2.y.cog", "Spot2.z.cog", "Spot2.r.cog"))

dt.rf.dist[,`:=`(Channel1="Red",
                 Channel2="Far Red")]

# Stitch everything together
dt.all.dist <- rbindlist(list(dt.gr.dist, dt.gf.dist, dt.rf.dist))

# Calculate distances as needed
dt.all.dist[,`:=`(SpotDist = sqrt((Spot1.x.cog-Spot2.x.cog)^2+(Spot1.y.cog-Spot2.y.cog)^2))]

setkey(dt.all.dist, AssayIndex, nrow, ncol, FieldIndex, CellIndex, SpotIndex1, 
                    Channel1, Channel2, 
                    Green_Probe, Red_Probe, FarRed_Probe, chr, Cell_Type, Culture_Condition)
```

Proximity calculations. **Important: this calculations find the closest Green/Red and Green/FarRed pairs on a per-green-spot basis and the closest Red/FarRed  pairs (by calculating the the minimum distance) on a per Red Spot basis**.

```{r proximityR-G, results='hide'}
dt.all.dist[,SpotDist.micron := SpotDist*xyres]

dt.min <- dt.all.dist[,.SD[which.min(SpotDist),], by = key(dt.all.dist)]
```

## Calculate equi-area shell!

```{r equiAreaCalc}
dt.min[,`:=`(AreaShell.spot1.COG = 4,
             AreaShell.spot2.COG = 4)]

dt.min[Spot1.r.cog < sqrt(0.8), AreaShell.spot1.COG:= 3]
dt.min[Spot2.r.cog < sqrt(0.8), AreaShell.spot2.COG:= 3]

dt.min[Spot1.r.cog < sqrt(0.6), AreaShell.spot1.COG:= 2]
dt.min[Spot2.r.cog < sqrt(0.6), AreaShell.spot2.COG:= 2]

dt.min[Spot1.r.cog < sqrt(0.4), AreaShell.spot1.COG:= 1]
dt.min[Spot2.r.cog < sqrt(0.4), AreaShell.spot2.COG:= 1]

dt.min[Spot1.r.cog < sqrt(0.2), AreaShell.spot1.COG:= 0]
dt.min[Spot2.r.cog < sqrt(0.2), AreaShell.spot2.COG:= 0]

```

```{r pullProbeIDs}
dt.min[Channel1=="Green"&Channel2=="Red",`:=`(Probe1 = min(Green_Probe, Red_Probe), Probe2 = max(Green_Probe, Red_Probe)), by=list(nrow,ncol)]
dt.min[Channel1=="Green" & Channel2=="Far Red",`:=`(Probe1 = min(Green_Probe, FarRed_Probe), Probe2 = max(Green_Probe, FarRed_Probe)), by=list(nrow,ncol)]
dt.min[Channel1=="Red"&Channel2=="Far Red",`:=`(Probe1 = min(Red_Probe, FarRed_Probe), Probe2 = max(Red_Probe, FarRed_Probe)), by=list(nrow,ncol)]
```

Write output table with spot-spot distance and radial position:
```{r outputData}
ColsForPairs <- c("AssayIndex", "nrow", "ncol",
                  "FieldIndex", "CellIndex", "SpotIndex1", "SpotIndex2", 
                  "Channel1", "Channel2", "Probe1", "Probe2",
                  "SpotDist", "SpotDist.micron", "Spot1.r.cog", "Spot2.r.cog",
                  "AreaShell.spot1.COG", "AreaShell.spot2.COG",
                  "PercDiploidGreen", "PercDiploidRed", "PercDiploidFarRed",
                  "Green_Probe", "Red_Probe", "FarRed_Probe", "chr", 
                  "Cell_Type", "Culture_Condition")

write.table(dt.min[,..ColsForPairs], file="Pairs.txt", sep="\t", row.names=FALSE, col.names=TRUE)

dt.all.sel <- rbindlist(list(dt.gr.sel, dt.gf.sel[color=="Far Red",]))
ColsForSpots <- c("AssayIndex", "nrow", "ncol", "color",
                  "FieldIndex", "CellIndex", "SpotIndex", 
                  "x.cog", "y.cog", "r.cog",  
                  "GreenSpotCount", "RedSpotCount", "FarRedSpotCount",
                  "PercDiploidGreen", "PercDiploidRed", "PercDiploidFarRed",
                  "Green_Probe", "Red_Probe", "FarRed_Probe", "chr", 
                  "Cell_Type", "Culture_Condition")
dt.all.sel <- dt.all.sel[,..ColsForSpots]
write.table(dt.all.sel, file="Spots.txt", sep="\t", row.names=FALSE, col.names=TRUE)
```

```{r setThemeandPalette, include='false'}
theme_set(theme_minimal())
theme_update(axis.text.x=element_text(size=16, angle = -90, hjust = 0),
            axis.text.y=element_text(size=16),
            axis.title.x=element_text(size=24),
            axis.title.y=element_text(size=24, angle=90),
            legend.text=element_text(size=16),
            legend.title=element_text(size=16),
            strip.text=element_text(size=16))
```

First of all, some quality control on the spot numbers.
```{r SpotsNumber_Green, echo=FALSE, fig.width = 12}
count.spots <- ggplot(dt.cell, aes(x = GreenSpotCount, y = ..density..)) 

count.spots  + geom_histogram(fill = "#56B4E9", color = "#999999", binwidth = 1) + 
                 ylab('Density') + 
                 coord_cartesian(xlim = c(-1,8)) +
                 scale_x_continuous(breaks = 0:8) +
                 xlab('Number of Green FISH Signals per Cell') + 
                 facet_grid(nrow ~ ncol) 
```

```{r SpotsNumber_Red, echo=FALSE, fig.width = 12}
count.spots <- ggplot(dt.cell, aes(x = RedSpotCount, y = ..density..)) 

count.spots  + geom_histogram(fill = "#56B4E9", color = "#999999", binwidth = 1) + 
                 ylab('Density') + 
                 coord_cartesian(xlim = c(-1,8)) +
                 scale_x_continuous(breaks = 0:8) +
                 xlab('Number of Red FISH Signals per Cell') + 
                 facet_grid(nrow ~ ncol) 
```

```{r SpotsNumber_FarRed, echo=FALSE, fig.width = 12}
count.spots <- ggplot(dt.cell, aes(x = FarRedSpotCount, y = ..density..)) 

count.spots  + geom_histogram(fill = "#56B4E9", color = "#999999", binwidth = 1) + 
                 ylab('Density') + 
                 coord_cartesian(xlim = c(-1,8)) +
                 scale_x_continuous(breaks = 0:8) +
                 xlab('Number of Far Red FISH Signals per Cell') + 
                 facet_wrap(Cell_Type ~ FarRed_Probe) 
```

Histogram plotting everything all at once like a fool: 

```{r AllDistHist,  echo=FALSE, fig.height = 6, fig.width=10}
gr.hist2D <- ggplot(dt.min[nrow %in% c(2,3,4,7,8,9,11,12,13),], 
                    aes(x = SpotDist.micron, y = ..density.., fill=interaction(Channel1, Channel2))) 


gr.hist2D + geom_density(alpha = 0.3) + 
            ylab('Density') + 
            facet_grid(interaction(Green_Probe, Red_Probe, FarRed_Probe)~Cell_Type, scales="free") + 
            coord_cartesian(xlim = c(-0.1, 7.5)) +
            xlab('2D distance (um)')
```

```{r AllDistHist_ByCellType,  echo=FALSE, fig.height = 8, fig.width=10}
gr.hist2D <- ggplot(dt.min, aes(x = SpotDist.micron, y = ..density.., fill=Cell_Type)) 


gr.hist2D + geom_density(alpha = 0.3) + 
            ylab('Density') + 
            facet_wrap(Probe1~Probe2, scales="free") + 
            coord_cartesian(xlim = c(-0.1, 7.5), ylim=c(0,1)) +
            xlab('2D distance (um)')
```

```{r AllDistHist_Paneled,  echo=FALSE, fig.height = 12, fig.width=30}
gr.hist2D <- ggplot(dt.min, aes(x = SpotDist.micron, y = ..density.., fill=chr)) 


gr.hist2D + geom_density(alpha = 0.3) + 
            ylab('Density') + 
            facet_wrap(Probe1~Probe2, scales="free") + 
            coord_cartesian(xlim = c(-0.1, 7.5)) +
            xlab('2D distance (um)')
```


```{r Hist_ByCOGShell_spot1,  echo=FALSE, fig.height = 12, fig.width=24}
gr.hist2D <- ggplot(dt.min[Probe1== 52,], 
                    aes(x = SpotDist.micron, y = ..density.., fill=as.factor(AreaShell.spot1.COG))) 


gr.hist2D + geom_density(alpha = 0.3) + 
            ylab('Density') + 
            facet_grid(Cell_Type~Probe2, scales="free") + 
            scale_fill_brewer("Area Shell (spot 1)", type="div", palette=3) +
            coord_cartesian(xlim = c(-0.1,6), ylim=c(0,1)) +
            xlab('2D distance (um)')
```


```{r Hist_ByCOGShell_spot2,  echo=FALSE, fig.height = 12, fig.width=24}
gr.hist2D <- ggplot(dt.min[Probe1==52,], 
                    aes(x = SpotDist.micron, y = ..density.., fill=as.factor(AreaShell.spot2.COG))) 


gr.hist2D + geom_density(alpha = 0.3) + 
            ylab('Density') + 
            facet_grid(Cell_Type~Probe2, scales="free") + 
            scale_fill_brewer("Area Shell (spot 1)", type="div", palette=3) +
            coord_cartesian(xlim = c(-0.1,6), ylim=c(0,1)) +
            xlab('2D distance (um)')
```


```{r Scatter_DistvRad_spot1,  echo=FALSE, fig.height = 8, fig.width=12}
gr.hist2D <- ggplot(dt.min, 
                    aes(x = SpotDist.micron, y = Spot1.r.cog)) 


gr.hist2D +  stat_binhex(bins=50) + geom_point(color="#d95f02", alpha=0.1) +
            scale_fill_gradient(low="#FFFFFF", high="#150063") +
            facet_grid(Cell_Type ~ interaction(Probe1,Probe2), scales="free") + 
            scale_x_continuous('2D distance (um)', limits=c(0,3))+
            scale_y_continuous('Radial Position (spot 1; transformed)', limits=c(0,1))
```

```{r Scatter_DistvRad_spot2,  echo=FALSE, fig.height = 8, fig.width=12}
gr.hist2D <- ggplot(dt.min, 
                    aes(x = SpotDist.micron, y = Spot2.r.cog)) 


gr.hist2D +  stat_binhex(bins=50) + geom_point(color="#d95f02", alpha=0.1) +
            scale_fill_gradient(low="#FFFFFF", high="#150063") +
            facet_grid(Cell_Type ~ interaction(Probe1, Probe2), scales="free") + 
            scale_x_continuous('2D distance (um)', limits=c(0,3))+
            scale_y_continuous('Radial Position (spot 2; transformed)', limits=c(0,1))
```

Document the information about the analysis session
```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```